Analyzing the impact of social attributes on the success of commit integration

### 2017-02-20 Paper/MSRChallenge2017.tex
added a tad bit more to the decision tree classifer description

\paragraph{Metric}
Because decision trees are well tested and easy to interpret, we used a decision
tree classifier to create models which predict build integration success. 
The first model was generated with only
the technical factors, that provide insight on the complexity of the commit, 
to understand how well technical factors predicted build
success.  We then added the social factors to the technical factors to determine
the influence of additional social factors on predicting build success.
We evaluate the predictive power of these two 
models with 10-fold cross validation and determine the effects of adding social
factors when predicting build integration success.

>>>>

\paragraph{Metric}
Because decision trees are well tested supervised classifiers and easy to interpret, we used a decision
tree classifier to create models which predict build integration success. 
The first model was generated with only
the technical factors, that provide insight on the complexity of the commit, 
to understand how well technical factors predicted build
success.  We then added the social factors to the technical factors to determine
the influence of additional social factors on predicting build success.
We evaluate the predictive power of these two 
models with 10-fold cross validation and determine the effects of adding social
factors when predicting build integration success.
